Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-03-16 paper/rei.tex
All plots done.

\begin{figure}
\includegraphics[width=0.40\textwidth]{plots/plot_m1_m2_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_0930_vs_pl18_pc_zmax30_pliklite_srollv2_1015.pdf}
\caption{A zoomed-in of Fig.~\ref{fig:plot_mjs_2018_vs_2015} on the best constrained $m_1-m_2$ PC plane. We compare the Planck 2015 (gray) to the Planck 2018 constraints using two different low-$\ell$ $EE$ likelihoods: the \texttt{simall\_EE} likelihood (red) and the \texttt{srollv2} likelihood (blue). The \texttt{srollv2} likelihood used better foreground removal and is what we use as our fiducial results throughout this paper. 
}
\label{fig:plot_m1m2_2015_vs_2018}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Comparison of the 68\% and 95\% C.L. constraints on the cumulative optical depth in the tanh model (described in \refsec{example1}) between the full Planck likelihoods (shaded bands), our effective likelihoods in the KDE mode (blue solid) and Gaussian mode (black dashed). The effective likelihoods results oscillate around zero at high-z because of the truncated representation of the models at 5 PCs (enough to represent any observable effects in the data). While the Gaussian approximation performs fairly well, the more complete KDE mode gives a slightly more accurate 95\% limits on the total optical depth. \ch{add numbers in caption: 95\% (0.039, 0.02), best-fit (0.05290344, 0.005859431)}}
%double check plot, upper and lower limits seem to cross?
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.48\textwidth]{results/cosmomc_kde/taulo_prior_test/plot_xez_taulo_0p04_tauhi_0p02.png}
\caption{Example ionization history $x_e(z)$ for the high-$z$ model of \refsec{example2}. In addition to a tanh transition at low-redshift as in \refsec{example1}, there is an additional ionization plateau at high redshifts with a fixed transition at $z_t = 28$ and $\Delta z = 1$. This is a toy model constructed for illustration purposes only. Here we show the best-fit model in the Planck 2018 data $(\taulo, \tauhi) = (XX, XX)$, as well as  a model at the 95\% C.L. $(\taulo, \tauhi) = (XX, XX)$ (see also Fig.~\ref{two_parameter_model_2}  \wh{place x's on the models plotted in that plot}). \ch{Include 2nd helium in the plot.}
}
\label{fig:two_step_model}
\end{figure}

@@

\begin{figure}[t]
%\includegraphics[width=0.47\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.pdf}
\caption{\ch{Need to fix this plot.}   Comparison of the marginalized posteriors and the 2D 68\% and 95\% C.L. contours for the two-step model  described in \refsec{example2} between different likelihoods: The full Planck likelihoods (shaded), the effective likelihoods in the KDE mode with f = 0.14 (blue solid) and in the Gaussian approximation mode (black dashed). The results agree well with each other. As in Fig.~\ref{fig:tanh}, both the KDE and Gaussian modes agree very well with the full likelihood results, with the KDE  contours being slightly broader as expected.
}
\label{fig:two_parameter_model_2D}
\end{figure}

@@

%\begin{figure}
%\includegraphics[\textwidth]{results/direct_mcmc/two_parameter_model/tauhi_taulo_chains/pl18_tanh_highz_test2_run1_tri.png}
%\caption{Direct MCMC chains of the two-parameter model with \tauhi and \taulo: triangle plot of \tauhi and \taulo. The marginalized 1D constraints are \taulo = $0.0516 \pm 0.0076$, \tauhi = $0.0100 \pm   0.0066$. The ML model is \taulo = 0.0543 and \tauhi = 0.0054 corresponding to $z_{\rm re} = 7.68$ and $x_{e, \mathrm{min}} = 0.021$.
%}
%\label{fig:two_parameter_model_2D_plot}
%\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.48\textwidth]{plots/plot_m1_m2_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_0930_vs_pl18_pc_zmax30_pliklite_srollv2_1015.pdf}
\caption{A zoomed-in of Fig.~\ref{fig:plot_mjs_2018_vs_2015} on the best constrained $m_1-m_2$ PC plane. We compare the Planck 2015 (gray) to the Planck 2018 constraints using two different low-$\ell$ $EE$ likelihoods: the \texttt{simall\_EE} likelihood (red) and the \texttt{srollv2} likelihood (blue). The \texttt{srollv2} likelihood used better foreground removal and is what we use as our fiducial results throughout this paper. \ch{this plot is done.} 
}
\label{fig:plot_m1m2_2015_vs_2018}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Comparison of the 68\% and 95\% C.L. constraints on the cumulative optical depth in the tanh model (described in \refsec{example1}) between the full Planck likelihoods (shaded bands), our effective likelihoods in the KDE mode (blue solid) and Gaussian mode (black dashed). The effective likelihoods results oscillate around zero at high-z because of the truncated representation of the models at 5 PCs (enough to represent any observable effects in the data). While the Gaussian approximation performs fairly well, the more complete KDE mode gives a slightly more accurate 95\% limits on the total optical depth. \ch{this plot is done.}}
%double check plot, upper and lower limits seem to cross?
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.48\textwidth]{paper/plots/plot_xe_tanh_highz.pdf}
\caption{Example ionization history $x_e(z)$ for the high-$z$ model of \refsec{example2}. In addition to a tanh transition at low-redshift as in \refsec{example1}, there is an additional ionization plateau at high redshifts with a fixed transition at $z_t = 28$ and $\Delta z = 1$. This is a toy model constructed for illustration purposes only. Here we show the best-fit model in the Planck 2018 data $(\taulo, \tauhi) = (0.053, 0.006)$, as well as  a model at the 95\% C.L. $(\taulo, \tauhi) = (0.039, 0.020)$ (see also Fig.~\ref{fig:two_parameter_model_2D}). \ch{CH: This plot is done}}
%best-fit (0.05290344, 0.005859431)
%95%CL (0.039, 0.02) 
\label{fig:two_step_model}
\end{figure}

@@

\begin{figure}[t]
%\includegraphics[width=0.47\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.pdf}
\caption{Comparison of the marginalized posteriors and the 2D 68\% and 95\% C.L. contours for the two-step model  described in \refsec{example2} between different likelihoods: The full Planck likelihoods (shaded), the effective likelihoods in the KDE mode with f = 0.14 (blue solid) and in the Gaussian approximation mode (black dashed). The results agree well with each other. As in Fig.~\ref{fig:tanh}, both the KDE and Gaussian modes agree very well with the full likelihood results, with the KDE  contours being slightly broader as expected. \ch{To add in caption: best-fit model in the Planck 2018 data $(\taulo, \tauhi) = (0.053, 0.006)$, as well as  a model at the 95\% C.L. $(\taulo, \tauhi) = (0.039, 0.020)$}  \ch{Otherwise this plot is done.}
}
\label{fig:two_parameter_model_2D}
\end{figure}

@@

%\begin{figure}
%\includegraphics[\textwidth]{results/direct_mcmc/two_parameter_model/tauhi_taulo_chains/pl18_tanh_highz_test2_run1_tri.png}
%\caption{Direct MCMC chains of the two-parameter model with \tauhi and \taulo: triangle plot of \tauhi and \taulo. The marginalized 1D constraints are \taulo = $0.0516 \pm 0.0076$, \tauhi = $0.0100 \pm   0.0066$. The ML model is \taulo = 0.0543 and \tauhi = 4 corresponding to $z_{\rm re} = 7.68$ and $x_{e, \mathrm{min}} = 0.021$.
%}
%\label{fig:two_parameter_model_2D_plot}
%\end{figure}
